Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-07 Paper.tex
Add detailed state channel description

\subsection{General work-flow}

@@

The connection flow as shown in figure 3, can be summarized
as follows:

\begin{itemize}
\item[] 1) The user associates the laptop with the WiFi hotspot.
\item[] 2) Once connected is redirected to the captive portal front-end.
\item[] 3) Front provisions MetaMask as Web3 provider.
\item[] 4) Front-end uses MetaMaskto allow the user
  to send value to the contract opening a \textit{state channel}
(\textit{see section below}).
\item[] 5-6) Signed transaction is relayed through a light Infura proxy listening
  on port 8545.
\item[] 7) Once transaction is confirmed, the back-end iptables controller
  start forwarding user's traffic.
\end{itemize}

>>>>

\subsection{Main connection workflow}

@@

To keep users' freedom of interrupt the service consumption
whenever they want and also avoid the overhead of transacting
many times with the smart contract authors have implemented
what is known as a state channel in a smart contract; this
makes possible keep control of the time fraction of the service
that's already consumed and at the same time cryptographically
guarantee that the smart contract is going to unlock the funds
when the provider desires to do so. State channels are a
standard pattern in most blockchain applications and in all cases
(\textit{independently of the complexity}) present three main
steps: opening, transaction and closing; project's implementation
described below:

\subsubsection{Channel opening}
The connection flow as shown in figure 3, can be summarized
as follows:

\begin{itemize}
\item[] 1) The user associates the laptop with the WiFi hotspot.
\item[] 2) Once connected is redirected to the captive portal front-end.
\item[] 3) Front provisions MetaMask as Web3 provider.
\item[] 4) Front-end uses MetaMaskto allow the user
  to send value to the contract
\item[] 5-6) Signed transaction is relayed through a light Infura proxy listening
  on port 8545.
\item[] 7) Once transaction is confirmed, the back-end iptables controller
  start forwarding user's traffic.
\end{itemize}

\subsubsection{Channel transactions}
Before sending the initial value transaction (\textit{in proportion with
  the duration of the service}) user's front-end generates an ephemeral elliptic curve
secp256k1 keypair and sends the public key to the contract to open the state channel.
Corresponding ephemeral private key is the one that's going to be used
to periodically (each 10 s approximately)
produce increasing value signatures proportional to the
service consumption ellapsed time. This signatures are being send to the
backend instead of the blockchain; backend verifies and validates the
signatures and stores the last one (\textit{the most valuable}).

\subsubsection{Channel closing}
At the end, when the connection time is exhausted or the backend
stops receiving channel transactions for approximately 60 seconds,
the backend sends the last seen transaction to the smart contract
using the method \texttt{closeChannel}; this method, when called
with a valid channel signature as parameter, unlocks user's original
funds and transfer the signed amount to the contract owner
(\textit{provider of the service}) and the corresponding return
to the user.
